\cursedforest\ - A Random Forest Implementation for ``Big'' and ``Wide'' Data \\ Supplementary Information

### 2017-04-24 doc/publications/plos16/supplementary_information.tex
updated BMI section with new model
updated BMD section
rewrite

\usepackage{geometry}
 \geometry{
 a4paper,
% total={210mm,297mm}
% }
 left=17mm,
 right=23mm,
 top=20mm, 
 bottom=20mm,
 }
\usepackage{url}
\usepackage{rotating}
\usepackage{natbib}
\usepackage{placeins}
\usepackage{longtable}
\usepackage[latin1]{inputenc}
\usepackage{multirow}
\usepackage{hyperref}
%\usepackage{showframe}
\usepackage{pdflscape}
%\usepackage{pbox}
\usepackage{xcolor}
\usepackage{amsmath}
\usepackage{rotating}
\usepackage{multicol}
\usepackage{caption}

@@

\section{supplementary Information for Section 4.1}

@@

>>>>

\usepackage{geometry}
 \geometry{
 a4paper,
% total={210mm,297mm}
% }
 left=17mm,
 right=23mm,
 top=20mm, 
 bottom=20mm,
 }
\usepackage{url}
\usepackage{rotating}
\usepackage{natbib}
\usepackage{placeins}
\usepackage{longtable}
\usepackage[latin1]{inputenc}
\usepackage{multirow}
\usepackage{hyperref}
%\usepackage{showframe}
\usepackage{pdflscape}
%\usepackage{pbox}
\usepackage{xcolor}
\usepackage{amsmath}
\usepackage{rotating}
\usepackage{multicol}
\usepackage{caption}
\usepackage{subfigure}

@@

\section{Supplementary Information for Section 4.1}

\begin{figure}[tbhp]
  \begin{adjustwidth}{-2.00in}{0in}
    \caption{\textbf{Rank of literature assigned BMD genes}}
    \label{figure:knowngeneranks}
    \includegraphics[totalheight=6.5cm]{./figs/BMDgenes_landscape.pdf}
    \begin{flushleft}
      The figure shows the rank of the 100 literature assigned BMD genes. Each ball represents a SNP assigned to the closest gene with colour representing the distance (max 100 kb). The size shows the Gini impurity score with larger balls representing more important SNPs. The horizontal line separates the genes with SNPs amongst the Top 20 associated features. 
     \end{flushleft}
  \end{adjustwidth}
\end{figure}

\newpage

\section{supplementary Information for Section 4.2}

@@

\clearpage
\newpage

\section{supplementary Information for Section 4.2}

\begin{figure}[tbhp]
    \caption{\textbf{Rank of literature assigned BMD genes}}
    \label{figure:knowngeneranks}
    \includegraphics{./figs/BMDTop10K.pdf}
    \begin{flushleft}
      The figure shows the top 10,000 features by their rank and Gini impurity score (Importance). The line denotes the top 30 features which contains six novel loci. 
     \end{flushleft}
\end{figure}

\begin{figure}[tbhp]
    \caption{\textbf{Zoomplot in order of importance}}
    \label{figure:knowngeneranks}
    \includegraphics{./figs/new_10k_TNFRSF11B.pdf}
     \includegraphics{./figs/new_10k_CTNNB1.pdf}
    \begin{flushleft}
     \end{flushleft}
\end{figure}

\begin{figure}[tbhp]
    \caption{\textbf{Zoomplot in order of importance}}
    \label{figure:knowngeneranks}
      \includegraphics{./figs/new_10k_ZBTB40.pdf}
        \includegraphics{./figs/new_10k_IBSP.pdf}
    \begin{flushleft}
     \end{flushleft}
\end{figure}

\begin{figure}[tbhp]
    \caption{\textbf{Zoomplot of likely artefacts}}
    \label{figure:knowngeneranks}
      \includegraphics{./figs/EUR_chr13_66_4-67mb.pdf}
        \includegraphics{./figs/EUR_chr17_62_1-62_3mb.pdf}
    \begin{flushleft}
     \end{flushleft}
\end{figure}

\begin{figure}[tbhp]
    \caption{\textbf{Manhattan plot of PRODH and LINC01006}}
    \label{figure:knowngeneranks}
        \includegraphics{./figs/BMDTopWholeGenome_22.pdf}
      \includegraphics{./figs/BMDTopWholeGenome_7.pdf}
    \begin{flushleft}
     \end{flushleft}
\end{figure}
